Hypertension and microbiome

### 2019-05-14 articletwo.Rmd
GVLMA

@@

```{r abund salt lm group checks plot, fig.width=12, fig.height=8}
par(mfrow=c(3,3))
plot(gvlma::gvlma(lm.lacto.saltgroup), onepage = FALSE)
```

>>>>

```{r abund salt lm continuous checks table}
gvlma.table.plot(lm.lacto.duna)$table %>% kable
```

```{r abund salt lm continuous checks plot, fig.width=12, fig.height=8}
gvlma.table.plot(lm.lacto.duna)$plot %>% plot
```

@@

```{r abund salt lm group checks table}
gvlma.table.plot(lm.lacto.saltgroup)$table %>% kable
```

```{r abund salt lm group checks plot, fig.width=12, fig.height=8}
gvlma.table.plot(lm.lacto.saltgroup)$plot %>% plot
```
